Figures

### 2018-10-11 manuscript/figures.Rmd
finish out hierarchical demo figure
add 03_wetland_potential

>>>>

```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake chlorophyll and lake phosphorus. B) Number of lakes per region.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/02_hierarchical_demo-1.pdf")
```

```{r wetland_potential, fig.cap = "A) gSSURGO wetland potential versus National Wetlands Inventory cover. B) Locations of lakes where these number differ by more than 30 percent.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/03_wetland_potential-1.pdf")
```
